R for Clinical Study Reports and Submission

### 2021-12-02 slides/workshop-slides.Rmd
update slides

@@

@@

- `r2rtf` is an R package to create production-ready tables and figures in RTF format.
The R package is designed to

@@

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF file.
- enable pipes (`%>%`).
- only focus on the **table format**.
  Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

- Let's refer to examples in the [Section 2.4.2](https://r4csr.org/tlf-overview.html#r2rtf)

>>>>

- [ASA Princeton-Trenton Chapter](https://community.amstat.org/princetontrenton/home)
  + Please consider to be a member of our chapter.

<!--

@@

-->

@@

- `r2rtf` is an R package to create production-ready tables and figures in RTF format.

@@

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF format.
- enable pipes (`%>%`).
- only focus on the **table format**.
  + Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

- Let's refer to examples in the [Section 1.4.2](https://r4csr.org/tlf-overview.html#r2rtf)
